### 2019-06-03 initial/notes.tex
add Melnikov for full weak tides

\subsection{Consideration 4: Plotting Stable/Unstable manifolds}

@@

>>>>

\subsection{Consideration 4: Plotting Stable/Unstable
manifolds}\label{ss:melnikov_success}

@@

\subsection{Weak Perturber Hopping Distribution}

We consider in the weak perturber (strong coupling) regime, where $s_c < S_0$.
We will re-apply \autoref{ss:melnikov_success} to the weak tidal friction
equations to compute $P_{hop}(s_\star)$ where $\star$ denotes at separatrix
crossing. We will then seek an approximate form for $s_{\star}$ given arbitrary
initial conditions to predict the hopping probability distribution over initial
conditions. We only seek to solve Zone III (below separatrix) initial
conditions.

First, we note that the two integrals that I earlier called $\Delta_m, \Delta_c$
(garbage notation sorry) can be evaluated for the new weak tidal friction
integrals as follows:
\begin{align}
    \Delta_M &= \int\limits_0^{2\pi}\epsilon\p*{1 - \mu^2}
            \p*{\frac{2\Omega}{s} - \mu} \;\mathrm{d}\phi,\nonumber\\
        &\approx 2\pi \epsilon \frac{2\Omega}{s},\\
    \Delta_c &= \oint \epsilon \p*{1 - \mu^2}\p*{\frac{2\Omega}{s} - \mu}
            \;\mathrm{d}\phi,\nonumber\\
        &= 2\int\limits_0^{2\pi}
            \epsilon\sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi
            ,\nonumber\\
        &= 16\epsilon\sqrt{\eta \sin I}.
\end{align}
Recalling that $\eta = s_c/s$, we arrive at
\begin{equation}
    P_{hop} = \frac{4\sqrt{ss_c\sin I}}{\pi \Omega}.
\end{equation}

We evaluate the above at $s = s_\star$ for a given trajectory; we now want to
compute an analytical approximation to $s_\star$. Under a familiar set of
approximations, we can write
\begin{align*}
    \rd{s}{t} &\approx -s\epsilon,&
    \rd{\mu^{(1)}}{t} &\approx
    \begin{cases}
        -\epsilon\mu & \mu \gtrsim \frac{2\Omega}{s},\\
        \epsilon\frac{2\Omega}{s} & \mu \lesssim \frac{2\Omega}{s}.
    \end{cases}
\end{align*}
We have taken $\mu \ll \frac{s}{2\Omega}, 1 + \mu^2 \sim 1$ to arrive at the
first expression. The second expression hinges on the dominant term in
$\frac{2\Omega}{s} - \mu$; since $\mu < 0$ in Zone III, this term is always
positive.

Now, recall that we won't get a sensible answer this way, since the dynamics
near the separatrix $\abs*{\mu - \mu_4} \sim \sqrt{2\eta \sin I}$ are governed
by the piecewise map we defined before. However, if $s_c$ is truly small, then
the majority of the separatrix approach will be governed by the above flow. If
we also adopt the $\mu \lesssim \frac{2\Omega}{s}$ limit, in this spirit, then
an analytical solution can be approximated: we first observe that $\rd{\ln s}{t}
\gtrsim \rd{\mu^{(1)}}{t}$ in this limit by a factor of $\frac{s}{2\Omega}$, so
we approximate $s \approx s_0e^{-\epsilon t}$. This gives us
\begin{equation*}
    \mu(t) \approx \mu_0 + \frac{2\Omega}{s_0}\p*{e^{\epsilon t} - 1}.
\end{equation*}
If $\epsilon t \lesssim 1$, we can arrive at closed form $t_\star \approx
\frac{s_0 \Delta \mu}{2\Omega \epsilon}$. Note that $\Delta \mu$ here should be
calculated at $\phi = \pi$ since phase space is not flat there, unlike near the
saddle point (same motivation as usual). This gives us $s_\star = s_0
e^{-\frac{s_0 \Delta \mu}{2\Omega}}$. For a sample run at $s_0 = 10, s_c =
0.03, \mu_0 = -0.3, \phi_0 = 0$, this estimates $t_\star \sim 500$ which is
reasonably close to the measured $t_\star = 575$.

If we are to use this prescription, then we can obtain
\begin{equation}
    P_{hop}\p*{\mu_\pi(t = 0)}
        = \frac{4\sqrt{s_c \sin I s_0}}{\pi \Omega}
            e^{-\frac{s_0}{4\Omega}\Delta \mu_\pi}.
\end{equation}
What is noteworthy is the \emph{exponential} dependence on $\Delta \mu_\pi$; we
might expect similar behavior to manifest elsewhere thanks to the $\rd{\ln s}{t}
\sim \epsilon, \rd{\mu}{t} \propto \z*{-\epsilon \mu, \epsilon/s}$ in both
regimes of $\rd{\mu}{t}$. Further numerical testing to be performed.
